# Objectif de la formation {#intro}

`r colorize("Version provisoire et temporaire de la formation Insee 'Travail collaboratif avec R'","red")`

La formation vise à présenter la manière dont un projet collaboratif peut être mené avec `R` et la manière dont `Rstudio` facilite ce travail. Les compétences acquises au cours de cette formation sont les suivantes: 

* Bien utiliser `Rstudio` en utilisant les `Rprojects`;
* RMarkdown;
* Bien programmer en `R`;
* Utiliser `Git`;
* Développer des packages.

<!--------------
You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
------>